Gravitaitonal Wave Event Progenitor Synthesis

### 2022-05-25 src/tex/ms.tex
New title.

\newcommand{\flatiron}{\affiliation{Center for Computational Astrophysics, Flatiron Institute, New York, NY 10010, USA}}
\newcommand{\stonybrook}{\affiliation{Department of Physics and Astronomy, Stony Brook University, Stony Brook NY 11794, USA}}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{xcolor}
\usepackage{showyourwork}
\definecolor{rb4}{HTML}{27408B}
\newcommand{\kw}[1]{{\color{rb4}[KW: #1 ]}}
\newcommand{\wf}[1]{\textcolor{cyan}{WF: #1}}
\newcommand{\kb}[1]{\textcolor{pink}{#1}}
% \setlength{\floatsep}{0cm}
% \setlength{\textfloatsep}{0cm}
% \setlength{\belowcaptionskip}{-5pt}
% \setlength{\abovecaptionskip}{-5pt}
% Begin!
\begin{document}
\title{Backpropagating Gravitational wave events \kb{can we come up with something a bit more flashy?}}

@@

\begin{abstract}
One promising way to extract information about stellar astrophysics from
gravitational wave catalogs is to compare the catalog to the outputs of stellar
population synthesis modeling with varying physical assumptions.  The parameter
space of physical assumptions in population synthesis is high-dimensional and
the choice of parameters that best represents the evolution of a binary system
may depend on an as-yet-to-be-determined way on the system's properties. Indeed,
measuring the variation of population synthesis parameter settings with binary
properties is one of the principal ways to extract information about binary
evolution astrophysics from catalogs. Here we propose an inference pipeline to
simultaneously infer zero-age main sequence properties and population synthesis
parameter settings controlling modeled binary evolution from individual
gravitational wave observations of merging compact binaries.  Our pipeline can
efficiently explore the high-dimensional space of population synthesis settings
and progenitor system properties for each system in a catalog of gravitational
wave observations.  We apply our pipeline to observations in the third LIGO
Virgo Kagra Gravitational Wave Transient Catalog.  
We showcase the effectiveness of this pipeline with a detailed study
of the progenitor properties and population synthesis settings that produce
mergers like the observed GW150914.
\end{abstract}

>>>>

\newcommand{\flatiron}{\affiliation{Center for Computational Astrophysics, Flatiron Institute, New York, NY 10010, USA}}
\newcommand{\stonybrook}{\affiliation{Department of Physics and Astronomy, Stony Brook University, Stony Brook NY 11794, USA}}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{xcolor}
\usepackage{showyourwork}
\definecolor{rb4}{HTML}{27408B}
\newcommand{\kw}[1]{{\color{rb4}[KW: #1 ]}}
\newcommand{\wf}[1]{\textcolor{cyan}{WF: #1}}
\newcommand{\kb}[1]{\textcolor{pink}{#1}}
% \setlength{\floatsep}{0cm}
% \setlength{\textfloatsep}{0cm}
% \setlength{\belowcaptionskip}{-5pt}
% \setlength{\abovecaptionskip}{-5pt}
% Begin!
\begin{document}
\title{Gravitaitonal Wave Event Progenitor Synthesis}

@@

\begin{abstract}
One promising way to extract information about stellar astrophysics from
gravitational wave catalogs is to compare the catalog to the outputs of stellar
population synthesis modeling with varying physical assumptions.  The parameter
space of physical assumptions in population synthesis is high-dimensional and
the choice of parameters that best represents the evolution of a binary system
may depend on an as-yet-to-be-determined way on the system's properties. Indeed,
measuring the variation of population synthesis parameter settings with binary
properties is one of the principal ways to extract information about binary
evolution from catalogs. Here we propose an inference pipeline to simultaneously
infer zero-age main sequence properties and population synthesis parameter
settings controlling modeled binary evolution from individual gravitational wave
observations of merging compact binaries.  Our pipeline can efficiently explore
the high-dimensional space of population synthesis settings and progenitor
system properties for each system in a catalog of gravitational wave
observations.  We apply our pipeline to observations in the third LIGO Virgo
Kagra Gravitational Wave Transient Catalog.  
We showcase the effectiveness of this pipeline with a detailed study
of the progenitor properties and population synthesis settings that produce
mergers like the observed GW150914.
\end{abstract}
